Self Regulation Ontology Retest Analyses

### 2018-06-07 code/SRO_Retest_Analyses.Rmd
updated ddm analyses as contrast vs. non-contrast

@@

trial_num_rel_df %>%
  gather(key, value, -breaks) %>%
  ggplot(aes(breaks*10, value, color=factor(key, levels = c("acc_icc", "avg_rt_error_icc", "std_rt_error_icc", "avg_rt_icc", "std_rt_icc", "missed_percent_icc", "cue_switch_cost_rt_100_icc", "cue_switch_cost_rt_900_icc", "task_switch_cost_rt_100_icc", "task_switch_cost_rt_900_icc", "cue_switch_cost_acc_100_icc", "cue_switch_cost_acc_900_icc", "task_switch_cost_acc_100_icc", "task_switch_cost_acc_900_icc"), labels = c("Accuracy", "Average RT error", "SD RT error", "Average RT correct", "SD RT correct", "Missed percentage", "Cue switch cost RT (100)", "Cue switch cost RT (900)", "Task switch cost RT (100)", "Task switch cost RT (900)", "Cue switch cost Acc (100)", "Cue switch cost Acc (900)", "Task switch cost Acc (100)", "Task switch cost Acc (900)"))))+
  geom_point()+
  geom_line()+
  theme_bw()+
  xlab("Number of trials")+
  ylab("ICC")+
  theme(legend.title = element_blank(),
        legend.position = 'bottom')+
  scale_color_manual(values = cols,
                     breaks = c("Average RT error", "Accuracy", "SD RT error", "Missed percentage", "Average RT correct", "Cue switch cost Acc (100)", "SD RT correct", "Cue switch cost Acc (900)", "Cue switch cost RT (100)", "Task switch cost Acc (100)", "Task switch cost RT (100)", "Task switch cost Acc (900)", "Task switch cost RT (900)"))+
  ylim(-1,1)+
  guides(color = guide_legend(ncol=2, byrow=T))

@@

```{r warning=FALSE, message=FALSE}
tmp = measure_labels %>%
  mutate(dv = as.character(dv)) %>%
  filter(ddm_task == 1, 
         overall_difference != "condition",
         rt_acc != 'other') %>%
  drop_na() %>%
  left_join(boot_df[,c("dv", "icc", "spearman")], by = 'dv')

tmp %>%
  drop_na() %>% #try removing this in final release
  group_by(overall_difference, raw_fit, rt_acc) %>%
  summarise(icc_median = quantile(icc, probs = 0.5),
            icc_2.5 = quantile(icc, probs = 0.025),
            icc_97.5 = quantile(icc, probs = 0.975),
            spearman_median = quantile(spearman, probs = 0.5),
            spearman_2.5 = quantile(spearman, probs = 0.025),
            spearman_97.5 = quantile(spearman, probs = 0.975),
            num_vars = n()/1000) %>%
  datatable() %>%
  formatRound(columns=c('icc_median', 'icc_2.5', 'icc_97.5', 'spearman_median', 'spearman_2.5', 'spearman_97.5'), digits=3)
```

```{r}
tmp_save = tmp %>%
  drop_na() %>% #try removing this in final release
  group_by(overall_difference, raw_fit, rt_acc) %>%
  summarise(icc_median = quantile(icc, probs = 0.5),
            icc_2.5 = quantile(icc, probs = 0.025),
            icc_97.5 = quantile(icc, probs = 0.975),
            num_vars = n()/1000) %>%
  ungroup() %>%
  mutate(overall_difference = as.character(overall_difference),
         raw_fit = as.character(raw_fit),
         rt_acc = as.character(rt_acc)) %>%
  arrange(-icc_median)

>>>>

Takeaways from this graph:
- Reliability estimates stabilize after about an eigthth of the trials (note that this might not be true for other model parameter estimates; here we are only looking at raw response time and accuracy measures)
- Only three measures that are not contrast measures have reliabilities >0
- All the other measures are basically completely unreliable (including the two 'meaningful variables' in the literature: the cue switch cost RT's)

@@

cols <- c("Accuracy" = '#084594', "Average RT error" = '#99000d', "Average RT correct" = '#ef3b2c', "Missed percentage" = '#2171b5', "Cue switch cost RT (100)" = '#fc9272', "Cue switch cost RT (900)" = '#fcbba1', "Task switch cost RT (100)" = '#fee0d2', "Task switch cost RT (900)" = '#fff5f0', "Cue switch cost Acc (100)" = '#4292c6', "Cue switch cost Acc (900)" = '#6baed6', "Task switch cost Acc (100)" = '#9ecae1', "Task switch cost Acc (900)" = '#c6dbef')

trial_num_rel_df %>%
  select(-std_rt_icc, -std_rt_error_icc)%>%
  gather(key, value, -breaks) %>%
  ggplot(aes(breaks*10, value, color=factor(key, levels = c("acc_icc", "avg_rt_error_icc", "avg_rt_icc", "missed_percent_icc", "cue_switch_cost_rt_100_icc", "cue_switch_cost_rt_900_icc", "task_switch_cost_rt_100_icc", "task_switch_cost_rt_900_icc", "cue_switch_cost_acc_100_icc", "cue_switch_cost_acc_900_icc", "task_switch_cost_acc_100_icc", "task_switch_cost_acc_900_icc"), labels = c("Accuracy", "Average RT error", "Average RT correct", "Missed percentage", "Cue switch cost RT (100)", "Cue switch cost RT (900)", "Task switch cost RT (100)", "Task switch cost RT (900)", "Cue switch cost Acc (100)", "Cue switch cost Acc (900)", "Task switch cost Acc (100)", "Task switch cost Acc (900)"))))+
  geom_point()+
  geom_line()+
  theme_bw()+
  xlab("Number of trials")+
  ylab("ICC")+
  theme(legend.title = element_blank(),
        legend.position = 'bottom')+
  scale_color_manual(values = cols,
                     breaks = c("Average RT correct", "Average RT error", "Cue switch cost RT (100)","Cue switch cost RT (900)", "Task switch cost RT (100)","Task switch cost RT (900)","Accuracy", "Missed percentage", "Cue switch cost Acc (100)", "Cue switch cost Acc (900)",  "Task switch cost Acc (100)",  "Task switch cost Acc (900)"))+
  ylim(-1,1)+
  guides(color = guide_legend(ncol=2, byrow=F))

@@

```{r warning=FALSE, message=FALSE}
tmp = measure_labels %>%
  mutate(dv = as.character(dv),
         contrast = ifelse(overall_difference == "difference", "contrast", "non-contrast")) %>%
  filter(ddm_task == 1, 
         #overall_difference != "condition",
         rt_acc != 'other') %>%
  drop_na() %>%
  left_join(boot_df[,c("dv", "icc")], by = 'dv')

tmp = tmp %>%
  drop_na() %>% #try removing this in final release
  group_by(contrast, raw_fit, rt_acc) %>%
  summarise(icc_median = quantile(icc, probs = 0.5),
            icc_2.5 = quantile(icc, probs = 0.025),
            icc_97.5 = quantile(icc, probs = 0.975),
            num_vars = n()/1000)

tmp %>% 
  datatable() %>%
  formatRound(columns=c('icc_median', 'icc_2.5', 'icc_97.5'), digits=3)
```

```{r}
tmp_save = tmp %>%
  ungroup() %>%
  mutate(contrast = as.character(contrast),
         raw_fit = as.character(raw_fit),
         rt_acc = as.character(rt_acc)) %>%
  arrange(-icc_median)
